Papers

### 2024-10-22 papers.qmd
typo
add preprint link
bugfix
updated patent

J.E. Borgert, J. Hannig$, **J.D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J.S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in accepted, 2024. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

## Patents
"Method and system for training an artifical neural network utilizing physics based knowledge" US Patent No. Applied

>>>>

J.E. Borgert, J. Hannig, **J.D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J.S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, accepted, 2024. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

## Patents
"Density-Based clustering of multidimensional Data" US Patent No. Applied

"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. Applied
